SLE martingales in coset conformal field theory

### 2012-06-10 AffineLieAlgebras/SLE/paper.tex
Sent improved version to JETP Letters.

For us it is convenient to use the map $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$, so the equation \eqref{eq:19} becomes
\begin{equation}
  \label{eq:20}
       d w _{t}= \frac{2dt}{w_{t} }-\sqrt{\kappa}\xi_{t}  
\end{equation}

@@

Now we need to consider the evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in the right-hand-side of equation (\ref{eq:1}) gives us
\begin{equation*}
  -\frac{2h_{i}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}.
\end{equation*}
We denote by $\mathcal{G}_{i}$ the generator of infinitesimal transformation of primary field $\phi_{i}$:$d\phi_{i}(w_{i}) = \mathcal{G}_{i}\phi_{i}(w_{i})$. We normalize additional $\left(\dim\gf\right)$-dimensional Brownian motion as $\mathbb  {E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$. The generator of field transformation is equal to
\begin{equation}
  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a:\mathcal{K}(t^{a},\tilde{t}^{b})=0}\left(d \theta ^{a} t^{a}_{i}\right)\right).
\label{eq:3}
\end{equation}
So we have fixed $A$-gauge by allowing random walk only in direction orthogonal to subalgebra $\af$.

 Ito formula  gives us an expression for the differential of $\mathcal{F}$ which should be zero due to martingale condition:
\begin{multline}
d \mathcal{F}_{\mathbb{H}_{t}}=\\ \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}\right)
\left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
      \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}\\=0
\label{eq:8}
\end{multline}
Substituting  definition \eqref{eq:3} we get 
\begin{equation}
  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}-
      \sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0,
  \label{eq:4}
\end{equation}
with
\begin{eqnarray*}
  \mathcal{L}_{-n}=\sum_{i}\left(\frac{(n-1)h_{i}}{(w_{i}-z)^{n}}-\frac{\partial_{w_{i}}}{(w_{i}-z)^{n-1}}\right),\\ \mathcal{J}^{a}_{{-n}}=-\sum_{i}\frac{t^{a}_{i}}{(w_{i}-z)^{n}};\; \tilde{\mathcal{J}}^{b}_{{-n}}=-\sum_{i}\frac{\tilde{t}^{b}_{i}}{(w_{i}-z)^{n}}.
\end{eqnarray*}
This equation is equivalent to the following algebraic condition on the boundary state $\varphi(0)\left|0\right>$:
\begin{multline}
  \label{eq:7}
  \left<0\left|\varphi(\infty)\phi_{1}(w_{1})\dots\phi_{2N}(w_{2N})\right.\right.\\
  \left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\\
\left.\varphi(0)|0\right>=0.
\end{multline}
Since the set $\{\phi_{i}\}$ consists of arbitrary primary fields we conclude that 
\begin{multline}
|\psi>=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\\
\cdot\varphi(0)|0>
\end{multline}
is a null-state. Now we act on $\psi$ by raising operators to get equations on $\kappa,\tau$. Since in a coset theory commutation relations of full chiral algebra are
\begin{equation}
  \label{eq:18}
\begin{array}{ll}
  L_{n}= L_{n}^{\gf}-L_{n}^{\af}, &\\
  \left[L_{n}^{\gf},J^{a}_{m}\right]= -m J^{a}_{n+m},&\\
  \left[L_{n}^{\gf},\tilde{J}^{b}_{m}\right]=-m\tilde{J}^{b}_{n+m},&\\
  \left[L_{n}^{\gf},L_{m}\right]=[L_{n}^{\gf},L_{m}^{\gf}]-[L_{n}^{\gf},L_{m}^{\af}]=&\\
  \quad =(n-m)L_{m+n}+\frac{c}{12}(n^{3}-n)\delta_{m+n,0},&
\end{array}
\end{equation}
 it is more convenient to act with $L_{2}^{\gf}$ and $\left(L_{1}^{\gf}\right)^{2}$. 
 Applying $L_{2}^{\gf}$ we get
\begin{equation*}
  L_{2}^{\gf}\psi= \left(-8 L_{0}-c+ 3 \kappa L_{0}+\frac{1}{2}\tau (k \dim\gf-x_{e}k\dim\af)\right) \varphi_{(\mu,\nu)}=0
\end{equation*}
We use $L_{0} \varphi_{(\mu,\nu)}=h_{(\mu,\nu)} \varphi_{(\mu,\nu)}$, with the conformal weight  $h_{(\mu,\nu)}= \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee}_{\gf})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k x_{e}+h^{\vee}_{\af})}\right)$ and the central charge $c=\frac{k\dim \gf}{k+h^{\vee}_{\gf}}-\frac{x_{e}k\dim \af}{x_{e} k+h^{\vee}_{\af}}$. This leads to the relation on $\kappa,\tau$:
\begin{equation}
  \label{eq:28} (3\kappa-8)h_{(\mu,\nu)}-c+\tau (k\dim\gf-x_{e}k\dim\af) =0.
\end{equation}
The second relation appears as a result of the $L_{1}^{\gf}$-action:
\begin{equation}
  \label{eq:21}
 -12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) + \tau
(C_{\mu}-\tilde{C}_{\nu})=0,
\end{equation}
 where $C_{\mu}=(\mu,\mu+2\rho)$ and $\tilde{C}_{\nu}=(\nu,\nu+2\rho_{\af})$ are the eigenvalues of the quadratic Casimir operators $\sum_{a}t^{a}t^{a}$ and $\sum_{b}\tilde{t}^{b}\tilde{t}^{b}$ of Lie algebras $\gf$ and $\af$.
Relations \eqref{eq:28},\eqref{eq:21} are the necessary conditions for CFT correlation functions to be SLE martingales.

>>>>

For us it is convenient to use the map $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$, so the equation \eqref{eq:19} becomes
\begin{equation}
  \label{eq:20}
       d w _{t}= \frac{2dt}{w_{t} }-\sqrt{\kappa}d\xi_{t}  
\end{equation}

@@

Now we need to consider the evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in the right-hand-side of equation (\ref{eq:1}) gives us
\begin{equation*}
  -\frac{2h_{i}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}.
\end{equation*}
We denote by $\mathcal{G}_{i}$ the generator of infinitesimal transformation of primary field $\phi_{i}$:$d\phi_{i}(w_{i}) = \mathcal{G}_{i}\phi_{i}(w_{i})$. We normalize additional $\left(\dim\gf\right)$-dimensional Brownian motion as $\mathbb  {E}\left[d\theta^{a}\; d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$. We also introduce the parameter $\tau$, which is the variance of this stochastic process. The generator of field transformation is equal to
\begin{equation}
  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a:\mathcal{K}(t^{a},\tilde{t}^{b})=0}\left(d \theta ^{a} t^{a}_{i}\right)\right).
\label{eq:3}
\end{equation}
So we have fixed $A$-gauge by allowing random walk only in direction orthogonal to subalgebra $\af$.

The differential of $\mathcal{F}$ should be zero due to martingale condition.  Ito formula is used to calculate the differential \cite{alekseev2010sle}. We need to include second order terms in  $\mathcal{G}_{i}$ since they contain squares of Brownian motion differentials $d\xi_{t},\; d\theta^{a}$ with the expectation values proportional to $dt$ ($\mathbb{E}[d\xi_{t}^{2}]=dt$):
\begin{multline}
d \mathcal{F}_{\mathbb{H}_{t}}=\\ \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}\right)
\left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
      \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}\\=0
\label{eq:8}
\end{multline}
Substituting  definition \eqref{eq:3} we get 
\begin{equation}
  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}-
      \sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)        \mathcal{F}_{\mathbb{H}}=0,
  \label{eq:4}
\end{equation}
with
\begin{eqnarray*}
  \mathcal{L}_{-n}=\sum_{i}\left(\frac{(n-1)h_{i}}{(w_{i}-z)^{n}}-\frac{\partial_{w_{i}}}{(w_{i}-z)^{n-1}}\right),\\ \mathcal{J}^{a}_{{-n}}=-\sum_{i}\frac{t^{a}_{i}}{(w_{i}-z)^{n}};\; \tilde{\mathcal{J}}^{b}_{{-n}}=-\sum_{i}\frac{\tilde{t}^{b}_{i}}{(w_{i}-z)^{n}}.
\end{eqnarray*}
This equation is equivalent to the following algebraic condition on the boundary state $\varphi(0)\left|0\right>$:
\begin{multline}
  \label{eq:7}
  \left<0\left|\varphi(\infty)\phi_{1}(w_{1})\dots\phi_{2N}(w_{2N})\right.\right.\\
  \left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\\
\left.\varphi(0)|0\right>=0.
\end{multline}
Since the set $\{\phi_{i}\}$ consists of arbitrary primary fields we conclude that 
\begin{multline}
|\psi>=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)\\
\cdot\varphi(0)|0>
\end{multline}
is a null-state. Now we act on $\psi$ by raising operators to get equations on $\kappa,\tau$. Since in a coset theory commutation relations of full chiral algebra are
\begin{equation}
  \label{eq:18}
\begin{array}{ll}
  L_{n}= L_{n}^{\gf}-L_{n}^{\af}, &\\
  \left[L_{n}^{\gf},J^{a}_{m}\right]= -m J^{a}_{n+m},&\\
  \left[L_{n}^{\gf},\tilde{J}^{b}_{m}\right]=-m\tilde{J}^{b}_{n+m},&\\
  \left[L_{n}^{\gf},L_{m}\right]=[L_{n}^{\gf},L_{m}^{\gf}]-[L_{n}^{\gf},L_{m}^{\af}]=&\\
  \quad =(n-m)L_{m+n}+\frac{c}{12}(n^{3}-n)\delta_{m+n,0},&
\end{array}
\end{equation}
 it is more convenient to act with $L_{2}^{\gf}$ and $\left(L_{1}^{\gf}\right)^{2}$. 
 Applying $L_{2}^{\gf}$ we get
\begin{equation*}
  L_{2}^{\gf}\psi= \left(-8 L_{0}-c+ 3 \kappa L_{0}+\frac{1}{2}\tau (k \dim\gf-x_{e}k\dim\af)\right) \varphi_{(\mu,\nu)}=0
\end{equation*}
We use $L_{0} \varphi_{(\mu,\nu)}=h_{(\mu,\nu)} \varphi_{(\mu,\nu)}$, with the conformal weight  $h_{(\mu,\nu)}= \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee}_{\gf})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k x_{e}+h^{\vee}_{\af})}\right)$ and the central charge $c=\frac{k\dim \gf}{k+h^{\vee}_{\gf}}-\frac{x_{e}k\dim \af}{x_{e} k+h^{\vee}_{\af}}$. This leads to the relation on $\kappa,\tau$:
\begin{equation}
  \label{eq:28} (3\kappa-8)h_{(\mu,\nu)}-c+\tau (k\dim\gf-x_{e}k\dim\af) =0.
\end{equation}
The second relation appears as a result of the $L_{1}^{\gf}$-action:
\begin{equation}
  \label{eq:21}
 -12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) + \tau
(C_{\mu}-\tilde{C}_{\nu})=0,
\end{equation}
 where $C_{\mu}=(\mu,\mu+2\rho)$ and $\tilde{C}_{\nu}=(\nu,\nu+2\rho_{\af})$ are the eigenvalues of the quadratic Casimir operators $\sum_{a}t^{a}t^{a}$ and $\sum_{b}\tilde{t}^{b}\tilde{t}^{b}$ of Lie algebras $\gf$ and $\af$.
Relations \eqref{eq:28},\eqref{eq:21} are the necessary conditions for CFT correlation functions to be SLE martingales.
